XXX

### 2012-03-24 paper/engNERwiki.tex
Related work --> Wikipedia and NER Evaluation intro

Named Entity Recognition (NER), the task of identifying Named Entities (NEs) in unstructured texts and classifying them into pre-selected classes, is one of the most important subtasks in many NLP tasks, such as Information Retrieval, Information Extraction or Machine Translation. The NER task was introduced with the 6th Message Understanding Conference (MUC) in 1995 (CITE). In MUC shared tasks the NER consists of three subtasks: entity names, temporal expressions and number expressions. However there is a general agreement in the NER community about the inclusion of temporal expressions and some numerical expressions such as amounts of money and other types of units, the most studied types are names of persons, locations and organizations. The fourth type, called "miscellaneous", is used in the CoNLL NER tasks in 2002 and 2003 (CITE), and includes proper names falling outside the three classic types. Since then, MUC and CoNLL datasets and annotation schemes have been the major standards applied in the field of NER.

@@

In this paper we present a kind of combination of the approaches mentioned above. We built NE-tagged corpora for English and Hungarian -- fully automatically generated from Wikipedia. Our goal was to create gold standard corpora which can serve as train, devel and test datasets for automatic NE-taggers.

@@

\section{Related Work}
% Wikify!
% stuff from Mining Meaning from Wikipedia
%NER and Wikipedia

@@

Wikipedia is recognized as one of the largest available collection of entities, and also as an external knowledge to improve the accuracy of NER. The most obvious utilization of Wikipedia for NER is extracting gazetteers containing person names, locations or organizations \cite{Toral:06}. Creating dictionaries of entities is also a common step of named entity disambiguation \cite{Bunescu:06,Cucerzan:07}. Not only supervised systems use lists generated from Wikipedia: Nadeau et al. \shortcite{Nadeau:06} use similar lists in an unsupervised NER system.

@@

not open access XXX

más nyelvekre is csinálták XXX

domain-specificity: not really

Szeged NER korpusz kicsi, ahhoz képest ez nagy

DBPediát előrébb

%Exploiting Wikipedia as external knowledge for NER:
%%-creating entity lists  
%%-disambiguating named entities
%%-automatic extraction of category labels from Wikipedia to improve the accuracy of a CRF-based NE-tagger \cite{Kazama:07}
%-entity ranking
%-typing named entities

%Automatic creation of training data from Wikipedia for NER:
%-classification of articles into CoNLL entity classes \cite{Nothman:08}

@@

\subsection{The DBpedia -- ConLL mapping}

% Introduction + entity -> class -> category.

@@

@@

>>>>

Named Entity Recognition (NER), the task of identifying Named Entities (NEs) in unstructured texts and classifying them into pre-selected classes, is one of the most important subtasks in many NLP tasks, such as Information Retrieval, Information Extraction or Machine Translation. The NER task was introduced with the 6th Message Understanding Conference (MUC) in 1995 \cite{Grishman:96}. In MUC shared tasks the NER consists of three subtasks: entity names, temporal expressions and number expressions. However there is a general agreement in the NER community about the inclusion of temporal expressions and some numerical expressions such as amounts of money and other types of units, the most studied types are names of persons, locations and organizations. The fourth type, called "miscellaneous'', is used in the CoNLL NER tasks in 2002 \cite{Tjong:02} and 2003 \cite{Tjong:03}, and includes proper names falling outside the three classic types. Since then, MUC and CoNLL datasets and annotation schemes have been the major standards applied in the field of NER.

@@

In this paper we present a kind of combination of the approaches mentioned above. We built NE-tagged corpora for English and Hungarian -- fully automatically generated from Wikipedia. %Our goal was to create gold standard corpora which can serve as train, devel and test datasets for automatic NE-taggers.

@@

\section{Wikipedia and NER}
% Wikify!
% stuff from Mining Meaning from Wikipedia
%NER and Wikipedia

@@

Wikipedia is recognized as one of the largest available collection of entities, and also as an external knowledge to improve the accuracy of NER. The most obvious utilization of Wikipedia for NER is extracting gazetteers containing person names, locations or organizations (e.g. Toral and Munoz \shortcite{Toral:06}). Creating dictionaries of entities is also a common step of named entity disambiguation \cite{Bunescu:06,Cucerzan:07}. Not only supervised systems use lists generated from Wikipedia: Nadeau et al. \shortcite{Nadeau:06} use similar lists in an unsupervised NER system.

@@

To our knowledge, such type of automatically built corpora are not freely available, with the only one exception of the Semantically Annotated Snapshot of the English Wikipedia \cite{Zaragoza:07}. It provides a wide range of linguistic information: POS tags, dependency labels, WordNet super senses and NE annotation according to WSJ and CoNLL tagsets. However, automatically NE-annotated corpus for Hungarian does not exist. Now we present freely available, automatically NE-tagged corpora for English and Hungarian.

%Szeged NER korpusz kicsi, ahhoz képest ez nagy

%DBPediát előrébb

@@

\subsection{The DBpedia -- ConLL mapping}
\label{dbpedia}
% Introduction + entity -> class -> category.

%Despite the aforementioned methods, we applied a new approach to recognize and classify NEs in the corpora generated from Wikipedia. We used the DBpedia ontology classes to map Wikipedia categories to standard NE tags (see more details in section \ref{dbpedia}).

@@

Having the obvious advantages, an automatically generated corpus can not serve as a gold standard dataset. Then what can we do with these so called "silver standard corpora" (SSC)? They can be very useful for improving NER in more ways: (a) for less commonly used languages, they can serve as training corpora in absence of gold standard datasets; (b) they can serve as (supplementary or independent) training sets for domains differing from newswire; (c) they can be sources of huge entity lists, and (d) feature extraction.

@@

\bibitem[\protect\citename{Zaragoza \bgroup et al.\egroup}2007]{Zaragoza:07}
H. Zaragoza and J. Atserias and M. Ciaramita and G. Attardi.
\newblock 2007.
\newblock Semantically Annotated Snapshot of the English Wikipedia v.1 (SW1).
\newblock \url{http://www.yr-bcn.es/semanticWikipedia}

\bibitem[\protect\citename{Tjong Kim Sang}2002]{Tjong:02}
Erik F. Tjong Kim Sang.
\newblock 2002.
\newblock Introduction to the CoNLL-2002 shared task: Language-independent named entity recognition.
\newblock In: {\em Proceedings of the 6th Conference on Natural Language Learning}, pages 1--4, Taipei, Taiwan.

\bibitem[\protect\citename{Tjong Kim Sang and De Meulder}2003]{Tjong:03}
Erik F. Tjong Kim Sang and Fien De Meulder.
\newblock 2003.
\newblock Introduction to the CoNLL-2003 shared task: Language-independent named entity recognition. 
\newblock In: {\em Proceedings of the 7th Conference on Natural Language Learning}, pages 142--147, Edmonton, Canada.

\bibitem[\protect\citename{Grishman and Sundheim}1996]{Grishman:96}
Ralph Grishman and B. Sundheim.
\newblock 1996.
\newblock Message Understanding Conference -- 6. 
\newblock In: {\em Proc. International Conference on Computational Linguistics}.
